An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-31 article.tex
Added table

>>>>

Each variable was logarithmically transformed and then centred around a mean of 0. The values of these variables were then divided by standard deviation creating a comparable ratio intrinsic to each variable. Table \ref{tab:summary} shows the summary statistics of each variable, to contextualise these ratios to real values.

\begin{table}[]
  \caption{Summary statistics of each continuous variable.}\label{tab:summary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cllll@{}}
          \toprule
          \textbf{Variable} & \textbf{Mean} & \textbf{\begin{tabular}[c]{@{}l@{}}Standard\\ Deviation\end{tabular}} & \textbf{Minimum} & \textbf{Maximum} \\ \midrule
          \textbf{Yield} & 7.757E+02 & 2.179E+03 & 1.000E+00 & 7.231E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          \textbf{Area Harvested} & 6.670E+05 & 1.337E+06 & 7.000E+02 & 2.436E+07 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          \textbf{Water Used} & 7.471E+06 & 5.646E+08 & 1.000E+00 & 4.268E+10 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          \textbf{Scope One Emissions} & 4.173E+04 & 8.571E+04 & 6.755E+00 & 2.110E+06 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          $\textbf{Yield}\over \textbf{Area}$ & 1.009E+01 & 8.127E+00 & 4.000E-02 & 8.634E+01 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          \textbf{Average Sale Price} & 1.477E+03 & 9.216E+02 & 1.600E+02 & 2.600E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          $\textbf{Average Sale Price} \over \textbf{Area Harvested}$ & 1.347E+02 & 5.711E+02 & 1.753E-01 & 2.979E+04 \\ \bottomrule
          \end{tabular}
  }
  \end{table}
